The Symmetry of Partner Modelling

### 2016-02-05 mutual-modeling.tex
Completed proof-reading

This study concerns a collaborative game that occurred in the physical
%ANON
%space~\citep{nova2006underwhelming}. We studied whether players build an accurate
space \textit{[citation removed for blind review]}. We studied whether players
build an accurate model of the path followed by their partners, assuming this
path reflected their problem solving strategy. We used an objective measure of
\gModel{A}{B}: the distance between where \A believes \B has been walking and
where \B actually went.  The main hypothesis concerned the effect of awareness
tools on group performance and on \gModel{A}{B}.

@@

{\sc CatchBob} is a mobile game in which groups of 3 players have to solve a
% ANON
%joint task. The game was played on EPFL campus. Participants had to find a
joint task. The game was played on our campus. Participants had to find a
virtual object (\emph{Bob}) and to ``catch'' it by forming a triangle around it.
Players used a Tablet PC that displayed a map of the campus and an indication of
their personal distance to Bob. Their annotations on the map were shared with
the two other players (\A could see what \B and \C wrote). These annotations
faded out after a few minutes to avoid covering the full display. The awareness
tool displayed as well the location of the two other players on the map. This
resulted in three conditions: the control condition (without tool) and two
experimental conditions: synchronous awareness (display of the current position
of each player) and asynchronous awareness (display of current position of each
player as well as their recent spatial trace).

@@

\gModel{A}{B} is the sum of errors made by \A about \B's paths. An error was
either drawing a place where the partner had not been or not drawing a place
where he/she had gone. One could argue that \gModel{A}{B} is biased by the
subjects' ability to translate their trajectories souvenir into a map drawing.
However, 85\% of subjects made no mistake at all when drawing their own path. We
therefore consider mistakes in their partners' path as being due to a lack of
mutual modelling accuracy instead of being due to spatial reasoning skills.

@@

\paragraph{Grounding criterion} The correlation between \gModel{A}{B} and the
task performance (path lengths) was low: 0.15. Using a post-hoc split on
\gModel{A}{B}, there is no significant difference between the performance of the
groups with high and low \gModel{A}{B}  ($F = 1.45, p = 0.24$). Conversely, a
post-hoc split of the groups according to their performance did not show
any significant differences on \gModel{A}{B} ($F = 1.16, p = 0.29$).

@@

This positive correlation observed in the symmetry question confirms the first
study.  In this case, this is actually more surprising given  the high
heterogeneity of spatial skills among adults~\citep{liben1981spatial}. This
result supports  $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$. The results regarding
$\Delta_2$ may support both  $\mathcal{H}_{2}$ and  $\mathcal{H}_{3}$  but
discards   $\mathcal{H}_{1}$  (if the modeller's skill would matter a lot,
$\Delta_2$ would be lower). Conversely, $\Delta_3$  supports $\mathcal{H}_{1}$
and  $\mathcal{H}_{3}$ but discards   $\mathcal{H}_{2}$  (if the modeller's
skill would matter a lot,  $\Delta_3$ would be lower). In summary, various
indices support the 3 hypotheses, which implies there is some truth in each of
them, but $\mathcal{H}_{3}$ is the only hypothesis that is not rejected by any
index. We may hence, with great caution, concluded that the social perspective
($\mathcal{H}_{3}$) is moderately reinforced by this second study. Since the
values of $\Delta_2$ and $\Delta_3$ are very similar, we do not interpret their
minor difference as evidence for a stronger role of the modeller
($\mathcal{H}_{1}$) or the modellee ($\mathcal{H}_{1}$).

We have however to bring some nuances to the social viewpoint
($\mathcal{H}_{3}$).  The main feature that can be associated to the team level
in this experiment is probably not the quality of their verbal interactions per
se (they interact mostly by drawing on a shared map), but rather the consistency
of  the spatial exploration strategy: a clear strategy facilitates memorizing
one's partner path.  One could argue whether the team strategy can be
dissociated from the team interactions quality or constitutes one of its
components.

@@

%ANON
%The aim of this unpublished\footnote{The data and statistical analyses of this
%study are available online:
%
%\url{https://github.com/chili-epfl/mutual-modelling-emotions-study}.}
The aim of this unpublished study was to evaluate the effect of media richness
on \Model{A}{B}{emotions}.  The hypothesis was that video communication would
lead to a better \gModel{A}{B} than audio only since emotions often impact on
facial expressions.

@@

Triads had to address an emotional societal debate: authorizing or not adoption
by homosexual couples. They worked on-line and had to structure their
argumentation with the shared concept map tool {\sc TeamWave} as illustrated in
Fig.~\ref{study3:argumentation_graph}. Ten groups had only an audio connection
while ten groups had audio and video. The video communication was provided by a
webcam and the software {\sc IVisit}. For the audio link, we used microphones,
headsets and the {\sc BattleCom} software. In the \emph{audio plus video}
condition, the screen was divided in three sections. The main part was devoted
to the concept map window, and the images of the two peers appeared next to it.
In the audio condition, this video zone was left empty so that the size of the
concept map was equal in each condition. The subjects were located in the same
room, separated by mobile walls. Despite their headsets, non-verbal audio cues
(\eg tapping the floor with feet) were possibly heard by the participants. The
task lasted in average 61 minutes.

@@

Sixty students (twenty triads) from the University of Geneva participated to
this experiment (36 women and 24 men). We formed groups of subjects who knew
each other: the task required the discussion of sensitive issues which required
to feel quite comfortable with peers. Since groups were formed \textit{a
priori}, we did not balance gender in each condition.

@@

The independent variable was the presence or not of a video link. The dependent
variable \gModel{A}{B} was measured subjectively from three questionnaires: in
the first one, \A described his/her own emotions \gmodel{A}{A}, while in the
two other questionnaire, \A described \B's and \C's emotions. The questionnaire
included 18 items (7-point Likert Scale) describing emotions labeled as
adjectives: \emph{anxious}, \emph{enthusiastic}, \emph{agitated}, \emph{proud},
\emph{excited}, \emph{quiet}, \emph{calm}, \emph{stressed}, \emph{bored},
\emph{upset}, \emph{relaxed}, \emph{irritated}, \emph{determined},
\emph{hostile}, \emph{active}, etc. \gmodel{A}{B} was modelled as a vector of 18
numerical values corresponding to their answers on each questionnaire items, and
\gModel{A}{B} was computed as the distance between the two vectors
\gmodel{A}{B} and \gmodel{B}{B}:

@@

The smaller the score, the \emph{more} accurate the model.

@@

\paragraph{Study-specific questions} Our hypothesis about media richness is
rejected: the average score for \model{A}{B}{emotions} was 1.25 ($SD = 0.53$) in
the audio+video condition and 1.09 ($SD = 0.41$) in the audio alone condition
($t=1.89, df=111, p = 0.062$): the average degree of accuracy of
\model{A}{B}{emotions} was hence \emph{higher} in the audio alone condition.

@@

@@

\paragraph{Rectangle question} We cannot address the relationship ($\Delta_4$)
between self and social accuracy here because we do not have an estimation of
self-accuracy: subjects describe their emotions but we have no way to check if
there are correct. By measuring \gModel{A}{B} on  18 emotional labels,
we can however have a glimpse about $\Delta_5$: how \Model{A}{B}{X} varies
according to X.  Fig.~\ref{study3:deg_m_values} shows the range of modelling
errors: the difference between \gmodel{A}{B} and \gmodel{B}{B}, on a scale of 7,
is 0.3 in average for the emotion \emph{discasted}, and up to 1.9 for the
emotion \emph{calm}. This is probably specific to the variety of scales  ($SD=
0.5$ for \emph{discated} versus $SD=0.7$ for \emph{calm}), our point is not to
interpret this too far, but to show that there are large variations even within one
area  (perceiving emotions). These variations somehow question the existence of
a general aptitude to model others ( $\mathcal{H}_{1}$).

@@

In this third study, the accuracy of mutual modelling  between two peers tend to
be symmetrical, which  supports $\mathcal{H}_{2}$ and ($\mathcal{H}_{3}$.)  This
result is contradicted by the fact that ($\Delta_2$) is not significant, which
rejects both $\mathcal{H}_{2}$ and, to a lower extent,,  $\mathcal{H}_{3}$.
Finally,  ($\Delta_3$) supports both  $\mathcal{H}_{1}$ and  $\mathcal{H}_{3}$.
In summary, this study brings some supports to  $\mathcal{H}_{3}$, but reveal
again that $\mathcal{H}_{3}$ is only part of the explanation.

Like the previous one, this study leads us to refine what we mean by quality of
interactions in $\mathcal{H}_{3}$. We  expected that the video channel would
help peers building a more accurate model of the each other's emotions.  The
results show the opposite: peers in the audio-only condition built more accurate
models, probably because they concentrated more on the shared concept map. This
confirms other studies that revealed that viewing what one's partner sees
(shared graphical editor) is more important than seeing each
other~\citep{gaver1993one,anderson1997impact}. Therefore, what is meant by the
quality of interactions is $\mathcal{H}_{3}$ is more than the linguistic features
of dialogue but includes the way these interactions are articulated to the task.

@@

The independent variable, script versus no-script, was implemented by the
difference of texts that individuals had to read.  The dependent variables were
the post-test scores, used to assess \Model{A}{B}{knowledge}. In phase 6,
participants were ask to estimate (7-point Likert scale) their own and their
partner's outcome knowledge with respect to each chapter of the learning
material. The order of questions about oneself and about the other was
counterbalanced across participants. 
%We measure \gModel{A}{B} in an objective
%(Eq.~\ref{eq:study4.1} and \ref{eq:study4.2}) as well as in a subjective way
%(Eq.~\ref{eq:study4.3}).
%
%\begin{multline} \label{eq:study4.1}
%    \Mdeg{A}{B}{knowledge} = 
%        \sum_{i=1}^{3} (\M{A}{B}{chapter_i} - score(B, chapter_i))
%\end{multline}
%
%\begin{multline} \label{eq:study4.2}
%    \Mdeg{A}{A}{knowledge} = 
%        \sum_{i=1}^{3}  (\M{A}{A}{chapter_i} - score(A, chapter_i))
%\end{multline}
%
%\begin{multline} \label{eq:study4.3}
%    \Mdeg{A}{B}{knowledge} = 
%        \sum_{i=1}^{3}  (\M{A}{B}{chapter_i} - \M{B}{A}{chapter_i})
%\end{multline}

@@

\paragraph{Study-specific questions} We performed a non-parametric Mann-Whitney
test on post-test scores for electric questions and a one-way ANOVA on scores
for ionic questions (Levene tests for homogeneity of variances): $p = 0.02$ and
$ns$, respectively. Results  did not show any significant difference between the
\emph{same information} (SI) condition and the \emph{complementary information}
(CI) condition, neither for electric questions ($U = 388.50, z = -0.88, ns$) nor
for ionic questions ($F(1, 58) = 0.17, ns$).  The effect of scripts on
\gModel{A}{B} was not significant ($F(1, 58) = 0.78, ns$) when considering the
absolute difference between \gModel{A}{B} and \B's post-test score. However, \A
tended underestimate \B's score in the SI condition ($M = -2.06$) and to
overestimate it in the CI condition ($M = 1.21$) ($F(1, 58) = 6.44, p<0.01$).
Regarding to \gModel{A}{A}, there was no significant difference between
conditions.

@@

\paragraph{Rectangle question} The correlation between \gmodel{A}{A} and
\gmodel{A}{B} ($\Delta_4$) is globally not significant ($r=0.05$) as well as not
significant in each condition: someone good at self-modelling is not necessarily
good at modelling someone else and vice-versa.  This seems to indicate that
partner modelling requires different skills than meta-cognition, despite their
similarity at some level of abstraction.

@@

How do we interpret the fact that the symmetry vanishes when peers receive
different texts to read before the task? One explanation would be the difficult
of mutual modelling when peers don't know what others read, but we found no
significance of \gModel{A}{A} between conditions. Since texts were partly
overlapping, another explanation is that, in absence of these initial common
grounds, mutual modelling requires \A to make evident to \B what \A thinks \B does
not know about A, which is the second level of modelling described in
$\mathcal{H}_{2}$ . A low symmetry means that some peers are better than others
at this second level of modelling, which supports the existence of such an
individual skill, as stated in  $\mathcal{H}_{2}$

@@

This study investigates if \Model{A}{B}{knowledge} is related to learning
outcomes by comparing teams with or without a knowledge awareness tool (KAT),
\ie a tool that informs \A about \B's knowledge as measured through a pre-test.

@@

The participants of the experimental condition group were provided with the KAT
on the bottom part of the screen (Fig.~\ref{study5:kat}): each line represents
the score obtained by the partner at the pre-test for a chapter. Participants
did not see they own score, but they usually started their discussion by
exchanging this information.

@@

\paragraph{Study-specific questions} The $t$-test reported a significant
difference between the KAT condition participants ($M = 13.4\%$) and the control
group [$M = 3.6\%, t(1, 60) = 2.73, p < 0.01$, Cohen's $d = 0.7$, medium to large
effect]: providing learners with cues about the prior-knowledge of their partner
enhances their collaborative learning. As a treatment check, we found a positive
and significant correlation between the amount of gazes on KAT (using eye
tracking devices) and the learning gains ($r(22) = 0.54, p = 0.01$). A detailed
analysis revealed that subjects look at KAT to assess their peer's credibility
when he/she provided new information.

The KAT has a significant effect on \gModel{A}{B}: peers more accurately
estimated their partners knowledge ($M = 1.11$) than those in the control
condition [$M = 0.98, t(1, 60) = 3.19, p < 0.01$, Cohen's $d = 0.83$, large
effect]. This is a trivial result since the KAT provided them with an initial
\gmodel{A}{B}. However, subjects have to predict the post-test score while the
KAT informed them about the pre-test score. Actually, pairs in the KAT condition
produced significantly more instances of 3 interesting categories of
interactions: (1) utterances asking about the other's knowledge such as ``Did
you understand how transmission works?'' (2) utterances describing one's own
knowledge (\gmodel{A}{A}) such as ``I don't remember the Ranvier's thing...''
and (3) elaborated utterances with rich contents,  These 3 categories provide
different account of \gModel{A}{B}: (1) as an effect of \A's effort to model
\B  ($\mathcal{H}_{1}$), (2) as \B's effort to give cues to \A about his own
knowledge  ($\mathcal{H}_{2}$) and (3) as an effect of the quality of
interaction  ($\mathcal{H}_{3}$) .

@@

\paragraph{Symmetry question} We did not find an intra-pair correlation ($ICC =
0.05, ns$), which discards  ($\mathcal{H}_{2}$) and  ($\mathcal{H}_{3}$). In
addition, the KAT supports the processing of modelling at the first level
($\mathcal{H}_{1}$) and not at the second level ($\mathcal{H}_{2}$). Hence the
fact that the KAT enhances  \gModel{A}{B}  brings additional supports to
$\mathcal{H}_{1}$. However, the analysis of verbal interactions find elements
that actually supports the three hypotheses.

 ($\mathcal{H}_{3}$)

@@

We found symmetry of the mutual model on 4 studies out of 5. In study 4, this
only applies to the control group (having read the same text before), which
corresponds to the situation of the 3 first studies.  Finding this symmetry per
se constitutes an interesting result as we don't know earlier studies who have
established this relationship. The problem is that this symmetry does not allow
use to discriminate  $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$. The second
hypothesis, the skill of helping one's peer to model oneself, is questioned by
study 3 where \C could be modelled  accurately by \A and not accurately by \B. The
same hypothesis is however supported by the results of study 2, and indirectly
by study 4.  This does not discard $\mathcal{H}_{1}$: even when we found
significant correlations, they were all below 0.50, not around 0.90.  Hence,
even of the quality of social interaction matters, there is obviously a large
part of individual variance within teams.

In other words, these studies do conclude that one hypothesis is right and the
others are wrong, which is per se the main contribution of this paper. We
started from the idea that partner modelling is essentially an individual skill
and that we therefore improve the quality of collaboration by providing the
so-called awareness tools, which act as some kind of prostheses for partner
modelling. This individual skill cannot be discarded.  Everyone has experienced
the pleasure of interacting with colleagues who answer precisely to the question
we asked them  and even guess the reason why we asked this question. Conversely,
everyone also experienced the frustration of someone referring about a third
person by his name, say Mike Smith,  while knowing perfectly that there is no
chance that we know this Mike Smith. The existence of these individual skills is
not denied by our studies; the novelty of this paper is to show, thanks to
symmetry values, that individual skills only account  for a part of the accuracy
in mutual modelling.

We acknowledge that the difference between these hypotheses is  rather
theoretical since the  process of modelling one's partner( $\mathcal{H}_{1}$)
and the process of helping one's partner to model oneself ($\mathcal{H}_{3}$) are
mediated by verbal interactions in the team. One could hardly imagine someone
managing a very accurate modelling despite the very bad quality of interactions.
There is a bidirectional causal link between the accuracy of mutual modelling
and the quality of interactions. This rather artificial distinction does however
participate to the more fundamental discussion of the role of individual and
social mechanisms in human cognition. In the field of social cognition, it is a
common place to state that ``the whole is greater than the sum of the parts''.
This refers to the emergence of team properties than cannot be reduced to the
set of individual contributions.  Our paper illustrates this emergence by
showing the symmetry of mutual modelling

These conclusions must be presented with multiple disclaimers. First, they
heavily rely on correlations; hence we cannot identify causal links. Second, we
faced hard methodological issues. Providing learners with on-task questionnaires
introduce a bias: they will pay more attention to their partners in the
remaining time. Providing them with ``after-task'' questionnaires implies mnemonic
and rationalization biases. The nature of mutual modelling implies methodological
challenges that call for new  measurement methods. We have promising results for
using eye tracking methods to address this challenge. 
Third, our results emerge from a post-hoc reinterpretation of studies
that addressed different research questions (media richness, awareness tools,
scripts,...). This diversity makes our results difficult to integrate, partly
contradictory. Nonetheless, this diversity gives some generalizability: mutual
modelling has been investigated in different contexts (virtual space versus real
space), with different groups sizes (pairs and triads) and different tasks.

>>>>

This study concerns a collaborative game that occurred in the physical
%ANON
%space~\citep{nova2006underwhelming}. We studied whether players build an accurate
space \textit{[citation removed for blind review]}. We studied whether players
build an accurate model of the path followed by their partners, assuming that this
path would reflect their problem solving strategy. We used an objective measure of
\gModel{A}{B}: the distance between where \A believes \B has been walking and
where \B actually went.  The main hypothesis concerned the effect of awareness
tools on group performance and on \gModel{A}{B}.

@@

{\sc CatchBob} is a mobile game in which groups of 3 players have to solve a
% ANON
%joint task. The game was played on EPFL campus. Participants had to find a
joint task. The game was played on our campus. Participants had to find a
virtual object (\emph{Bob}) and to ``catch'' it by forming a triangle around it.
The players used a Tablet PC that displayed a map of the campus and an indication of
their personal distance to Bob. Their annotations on the map were shared with
the two other players (\A could see what \B and \C wrote). These annotations
faded out after a few minutes to avoid covering the full display. The awareness
tool displayed as well the location of the two other players on the map. Three
conditions were considered: the control condition (without tool) and two
experimental conditions: synchronous awareness (display of the current position
of each player) and asynchronous awareness (display of current position of each
player as well as their recent spatial trace).

@@

\gModel{A}{B} is the sum of errors made by \A about \B's paths. An error was
either drawing a place where the partner had not been or not drawing a place
where he/she had gone. One could argue that \gModel{A}{B} is biased by the
subjects' ability to translate the memory of their trajectories into a map drawing.
However, 85\% of subjects made no mistake at all when drawing their own path.
We therefore consider mistakes in their partners' path as being due to a lack
of mutual modelling accuracy instead of being due to spatial reasoning skills.

@@

\paragraph{Grounding criterion} The correlation between \gModel{A}{B} and the
task performance (path lengths) was low: 0.15. Using a post-hoc split on
\gModel{A}{B}, we found no significant difference between the performance of the
groups with high and low \gModel{A}{B}  ($F = 1.45, p = 0.24$). Conversely, a
post-hoc split of the groups according to their performance did not show
any significant differences on \gModel{A}{B} ($F = 1.16, p = 0.29$).

@@

The positive correlation observed in the symmetry question confirms the first
study.  In this case, this was not expected given the high heterogeneity of
spatial skills among adults~\citep{liben1981spatial}. This result therefore
supports  $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$. The results regarding
$\Delta_2$ support both  $\mathcal{H}_{2}$ and  $\mathcal{H}_{3}$  but discards
$\mathcal{H}_{1}$: if the skill of the modeller would dominate -- as
hypothesized by $\mathcal{H}_{1}$, \gModel{A}{C}  and \gModel{B}{C} would tend
\emph{not} to be generally correlated.  Conversely, $\Delta_3$  supports
$\mathcal{H}_{1}$ and $\mathcal{H}_{3}$ but discards $\mathcal{H}_{2}$  (if the
modellee's skill were to dominate, \gModel{A}{B}  and \gModel{A}{C} would tend
\emph{not} to correlate). In summary, various indices support the 3 hypotheses,
which implies there is some truth in each of them, but $\mathcal{H}_{3}$ is the
only hypothesis that is not rejected by any index. We may hence, with great
caution, conclude that the social perspective ($\mathcal{H}_{3}$) is moderately
reinforced by this second study. Since the correlation values for $\Delta_2$ and
$\Delta_3$ are similar, we do not interpret their minor difference as evidence
for a stronger role of the modeller ($\mathcal{H}_{1}$) or the modellee
($\mathcal{H}_{2}$).

We have also to bring some nuances to the social viewpoint
($\mathcal{H}_{3}$).  The main feature that can be associated to the team level
in this experiment is probably not the quality of their verbal interactions per
se (they interact mostly by drawing on a shared map), but rather the consistency
of  the spatial exploration strategy: a clear strategy facilitates memorizing
one's partner path.  One could argue whether the team strategy can be
dissociated from the team interactions quality or constitutes one of its
components.

@@

%ANON
%The aim of this unpublished\footnote{The data and statistical analyses of this
%study are available online:
%
%\url{https://github.com/chili-epfl/mutual-modelling-emotions-study}.}
The aim of this unpublished study was to evaluate the effect of media richness
on \Model{A}{B}{emotions}.  The hypothesis was that video communication would
lead to a better \gModel{A}{B} than audio only since emotions often impact 
facial expressions.

@@

Triads had to address an emotional societal debate: authorizing or not adoption
by homosexual couples. They worked on-line and had to structure their
argumentation with the shared concept map tool {\sc TeamWave} as illustrated in
Fig.~\ref{study3:argumentation_graph}. Ten groups had only an audio connection
while ten groups had audio and video. The video communication was provided by a
webcam and the software {\sc IVisit}. For the audio link, we used microphones,
headsets and the {\sc BattleCom} software. In the \emph{audio + video}
condition, the screen was divided in three sections. The main part was devoted
to the concept map window, and the images of the two peers appeared next to it.
In the audio condition, this video zone was left empty so that the size of the
concept map was equal in each condition. The subjects were located in the same
room, separated by mobile walls. Despite their headsets, non-verbal audio cues
(\eg tapping the floor with feet) were possibly heard by the participants. The
task lasted in average 61 minutes.

@@

%ANON
%Sixty students (twenty triads) from the University of Geneva participated to
Sixty students (twenty triads) from \textit{[hidden for blind review]} participated to
this experiment (36 women and 24 men). We formed groups of subjects who knew
each other: the task required the discussion of sensitive issues which required
to feel quite comfortable with peers. Since groups were formed \textit{a
priori}, we did not balance gender in each condition.

@@

The independent variable was the presence or not of a video link. The dependent
variable \gModel{A}{B} was measured subjectively from three questionnaires: in
the first one, \A described his/her own emotions \gmodel{A}{A}, while in the
two other questionnaire, \A described \B's and \C's emotions. The questionnaire
included 18 items (7-point Likert Scale) describing emotions labeled as
adjectives: \emph{anxious}, \emph{enthusiastic}, \emph{agitated}, \emph{proud},
\emph{excited}, \emph{quiet}, \emph{calm}, \emph{stressed}, \emph{bored},
\emph{upset}, \emph{relaxed}, \emph{irritated}, \emph{determined},
\emph{hostile}, \emph{active}, etc. \gmodel{A}{B} was modelled as a vector of 18
numerical values corresponding to their answers on each questionnaire items, and
\gModel{A}{B} was computed as the distance between the two vectors
\gmodel{A}{B} and \gmodel{B}{B}, hence \emph{the smaller the score, the more
accurate the model}:

@@

@@

\paragraph{Study-specific questions} Our hypothesis about media richness is
rejected: the average degree of accuracy for \model{A}{B}{emotions} was 1.25
($SD = 0.53$) in the audio+video condition and 1.09 ($SD = 0.41$) in the audio
alone condition ($t=1.89, df=111, p = 0.062$). The smaller distance between
\model{A}{B}{emotions} and \model{B}{B}{emotions} in the audio condition shows
that, in average, the degree of accuracy of \model{A}{B}{emotions} is
\emph{higher} in the audio alone condition.

@@

\paragraph{Rectangle question} We cannot address the relationship $\Delta_4$
between self and social accuracy here because we do not have an estimation of
self-accuracy: subjects describe their own emotions but we have no way to check if
they are correct. By measuring \gModel{A}{B} on  18 emotional labels,
we can however have a glimpse about $\Delta_5$: how \Model{A}{B}{X} varies
according to X.  Fig.~\ref{study3:deg_m_values} shows the range of modelling
errors: the difference between \gmodel{A}{B} and \gmodel{B}{B}, on a scale of 7,
is 0.3 in average for the emotion \emph{discasted}, and up to 1.9 for the
emotion \emph{calm}. This is probably specific to the variety of scales  ($SD=
0.5$ for \emph{discated} versus $SD=0.7$ for \emph{calm}), our point is not to
interpret this too far, but to show that there are large variations even within one
area  (perceiving emotions). These variations still question the existence of
a general aptitude to model others ( $\mathcal{H}_{1}$).

@@

@@

In this third study, the accuracy of mutual modelling  between two peers tend to
be symmetrical, which  supports $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$. This
result is contradicted by the fact that $\Delta_2$ is not significant, which
contradicts both $\mathcal{H}_{2}$ and, to a lower extent, $\mathcal{H}_{3}$.
Finally, $\Delta_3$ supports both $\mathcal{H}_{1}$ and  $\mathcal{H}_{3}$: this
study brings some supports to  $\mathcal{H}_{3}$, but reveals again that
$\mathcal{H}_{3}$ is only part of the explanation.

Like the previous one, this study leads us to refine what we mean by ``quality
of interactions'' in $\mathcal{H}_{3}$. We  expected that the video channel
would help peers building a more accurate model of each other's emotions. The
results show the opposite: peers in the audio-only condition built more accurate
models, probably because they concentrated more on the shared concept map. This
confirms other studies that revealed that viewing what one's partner sees
(shared graphical editor) is more important than seeing each
other~\citep{gaver1993one,anderson1997impact}. Therefore, what is meant by the
quality of interactions in $\mathcal{H}_{3}$ is more than the linguistic
features of dialogue but includes the way these interactions are articulated to
the task.

@@

The independent variable, script versus no-script, was implemented by the
difference of texts that individuals had to read.  The dependent variables were
the post-test scores, used to assess \Model{A}{B}{knowledge}. In phase 6,
participants were asked to estimate (7-point Likert scale) their own and their
partner's outcome knowledge with respect to each chapter of the learning
material. The order of questions about oneself and about the other was
counterbalanced across participants. 
%We measure \gModel{A}{B} in an objective
%(Eq.~\ref{eq:study4.1} and \ref{eq:study4.2}) as well as in a subjective way
%(Eq.~\ref{eq:study4.3}).
%
%\begin{multline} \label{eq:study4.1}
%    \Mdeg{A}{B}{knowledge} = 
%        \sum_{i=1}^{3} (\M{A}{B}{chapter_i} - score(B, chapter_i))
%\end{multline}
%
%\begin{multline} \label{eq:study4.2}
%    \Mdeg{A}{A}{knowledge} = 
%        \sum_{i=1}^{3}  (\M{A}{A}{chapter_i} - score(A, chapter_i))
%\end{multline}
%
%\begin{multline} \label{eq:study4.3}
%    \Mdeg{A}{B}{knowledge} = 
%        \sum_{i=1}^{3}  (\M{A}{B}{chapter_i} - \M{B}{A}{chapter_i})
%\end{multline}

@@

\paragraph{Study-specific questions} We performed a non-parametric Mann-Whitney
test on post-test scores for the questions touching the electrical inner working
of neurons, and a one-way ANOVA on scores for chemistry-related questions
(Levene tests for homogeneity of variances): $p = 0.02$ and $ns$, respectively.
Results did not show any significant difference between the \emph{same
information} (SI) condition and the \emph{complementary information} (CI)
condition, neither for electrical-related questions ($U = 388.50, z = -0.88,
ns$), nor for chemistry-related questions ($F(1, 58) = 0.17, ns$).

The effect of scripts on \gModel{A}{B} was not significant ($F(1, 58) = 0.78,
ns$) when considering the absolute difference between \gModel{A}{B} and \B's
post-test score. However, \A tended to underestimate \B's score in the SI
condition ($M = -2.06$) and to overestimate it in the CI condition ($M = 1.21$)
($F(1, 58) = 6.44, p<0.01$).  Regarding \gModel{A}{A}, there was no
significant difference between conditions.

@@

\paragraph{Rectangle question} The correlation between \gModel{A}{A} and
\gModel{A}{B} ($\Delta_4$) is globally not significant ($r=0.05$), and neither
it is in each of the conditions: someone good at self-modelling is not necessarily
good at modelling someone else and vice-versa.  This seems to indicate that
partner modelling requires different skills than meta-cognition, despite their
similarity at some level of abstraction.

@@

How do we interpret the fact that the symmetry vanishes when peers receive
different texts to read before the task? One explanation would be the difficulty
of mutual modelling when peers do not know what the others read, but we found no
significance of \gModel{A}{A} between conditions. Since texts were partly
overlapping, another explanation is that, in absence of these initial common
grounds, mutual modelling requires \A to make evident to \B what \A thinks \B does
not know about A, which is the second level of modelling described in
$\mathcal{H}_{2}$ . A low symmetry means that some peers are better than others
at this second level of modelling, which supports the existence of such an
individual skill, as stated in  $\mathcal{H}_{2}$.

@@

This study investigates if \Model{A}{B}{knowledge} is related to learning
outcomes by comparing teams with or without a Knowledge Awareness Tool (KAT),
\ie a tool that informs \A about \B's knowledge as measured through a pre-test.

@@

The participants of the experimental condition group were provided with the
Knowledge Awareness Tool on the bottom part of the screen
(Fig.~\ref{study5:kat}): each line represents the score obtained by the partner
at the pre-test for a chapter. Participants did not see their own score, but they
usually started their discussion by exchanging this information.

@@

\paragraph{Study-specific questions} The $t$-test reported a significant
difference between the KAT condition participants ($M = 13.4\%$) and the control
group $M = 3.6\%$ [$t(1, 60) = 2.73, p < 0.01$, Cohen's $d = 0.7$, medium to large
effect]: providing learners with cues about the prior-knowledge of their partner
enhances their collaborative learning. As a treatment check, we found a positive
and significant correlation between the amount of gazes on KAT (using eye
tracking devices) and the learning gains ($r(22) = 0.54, p = 0.01$). A detailed
analysis revealed that the participants look at KAT to assess their peer's credibility
when he/she provided new information.

The KAT has a significant effect on \gModel{A}{B}: peers more accurately
estimated their partners knowledge ($M = 1.11$) than those in the control
condition $M = 0.98$ [$t(1, 60) = 3.19, p < 0.01$, Cohen's $d = 0.83$, large
effect]. This is a trivial result since the KAT provided them with an initial
\gmodel{A}{B}. However, the participants have to predict the post-test score while the
KAT informed them about the pre-test score. Actually, pairs in the KAT condition
produced significantly more instances of 3 interesting categories of
interactions: (1) utterances asking about the other's knowledge such as ``Did
you understand how transmission works?'' (2) utterances describing one's own
knowledge (\gmodel{A}{A}) such as ``I don't remember the Ranvier's thing...''
and (3) elaborated utterances with rich contents. These three categories provide
different account of \gModel{A}{B}: (1) as an effect of \A's effort to model
\B  ($\mathcal{H}_{1}$), (2) as \B's effort to give cues to \A about his own
knowledge ($\mathcal{H}_{2}$) and (3) as an effect of the quality of
interaction ($\mathcal{H}_{3}$) .

@@

\paragraph{Symmetry question} We did not find an intra-pair correlation ($ICC =
0.05, ns$), which does not support $\mathcal{H}_{2}$ and $\mathcal{H}_{3}$. In
addition, the KAT supports the processing of modelling at the first level
($\mathcal{H}_{1}$) and not at the second level ($\mathcal{H}_{2}$). Hence the
fact that the KAT enhances  \gModel{A}{B}  brings additional supports to
$\mathcal{H}_{1}$. However, the analysis of verbal interactions find elements
that actually supports the three hypotheses.

@@

We found a symmetry of the mutual models on 4 studies out of 5. In study 4, this
only applies to the control group (having read the same text before), which
corresponds to the situation of the 3 first studies. Evidencing this symmetry
constitutes \textit{per se} an interesting result as we are not aware of earlier
studies who have established this relationship.
Still, the symmetry alone does not allow to discriminate $\mathcal{H}_{2}$ from
$\mathcal{H}_{3}$. The second hypothesis (\ie mutual modelling is primarily
supported by the capacity of the modellee to help the modellers to form a
correct image of herself), is questioned by study 3 where \C could be modelled
accurately by \A and not accurately by \B. The same hypothesis is however
supported by the results of study 2, and indirectly by study 4.

This does not rule out entirely $\mathcal{H}_{1}$ (\ie partner modelling is
primarily a individual skill) either: even where we found significant
correlations, they were all below 0.50, not around 0.90.  Hence, even if the
quality of the social interaction matters, there is obviously a large part of
individual variance within teams.

In other words, these studies do not conclude that one hypothesis is right and the
others are wrong, and this is indeed the main contribution of this article. We
started from the idea that partner modelling is essentially an individual skill
and that we would therefore improve the quality of collaboration by providing 
awareness tools, as those tools would act as a kind of prosthesis for partner
modelling. The role and importance of this individual skill cannot be discarded:
everyone has experienced the pleasure of interacting with colleagues who answer precisely to the question
we asked them and even guess the reason why we asked this question. Conversely,
everyone also experienced the frustration of someone referring about a third
person by his name, say Mike Smith, while knowing perfectly that there is no
chance that we know this Mike Smith. In fact, the role of this individual skill is
not denied by our studies; the novelty of this paper is to show, thanks to
symmetry values, that individual skills only account for a part of the accuracy
in mutual modelling.

We acknowledge that the difference between these hypotheses is rather
theoretical since the  process of modelling one's partner $\mathcal{H}_{1}$ and
the process of helping one's partner to model oneself $\mathcal{H}_{2}$ are
mediated by verbal interactions in the team. One could hardly imagine someone
managing a very accurate modelling despite the very bad quality of interactions.
There is a bidirectional causal link between the accuracy of mutual modelling
and the quality of the interactions. This rather artificial distinction does
however participate to the more fundamental discussion of the role of individual
and social mechanisms in human cognition. In the field of social cognition, it
is a common place to state that ``the whole is greater than the sum of the
parts''.  This refers to the emergence of team properties than cannot be reduced
to the set of individual contributions. Our paper illustrates this emergence by
showing the symmetry of mutual modelling.

These conclusions must be presented with multiple disclaimers. First, they
heavily rely on correlations; hence we cannot identify causal links. Second, we
faced hard methodological issues. Providing learners with on-task questionnaires
introduces a bias: they will pay more attention to their partners in the
remaining time. Providing them with ``after-task'' questionnaires implies
mnemonic and rationalization biases. The nature of mutual modelling implies
methodological challenges that call for new measurement methods. We have
promising results for using eye tracking methods to address this challenge.
Third, our results emerge from a post-hoc reinterpretation of studies that
addressed different research questions (media richness, awareness tools,
scripts,...). This diversity makes our results difficult to integrate, partly
contradictory. Nonetheless, this diversity also incidentally provides some
generalizability: mutual modelling has been investigated in different contexts
(virtual space versus real space), with different groups sizes (pairs and
triads) and different tasks.
